Principle of least action as a software development method

### 2022-12-30 ms.tex
fix

The aim of this paper is translating the idea of action and PLA to software development and then show the implementation that uses Makefile+containers.
present the Makefile for python and tex for document generation and then the Makefile for website creation
creating an application (the target) sometimes requires creating tools (as intermediate targets) that can be use to reduce the development time (the path length to the target)
it is not just about minimizing time or being completely accurate in satisfying the requirements. A combination of these is required
the path to the target is the source code which can be evaluated with make check. The path should fulfill the needs of the developers and can change
the target is the application which can be reached with make. The target should fulfill the needs of the users and can change

@@

>>>>

The aim of this paper is translating the idea of action and PLA to software development and then show the implementation that uses Makefile+containers.
present the design and implementation of fswm, then the Makefile for python and tex for document generation and then the Makefile for website creation
creating an application (the target) sometimes requires creating tools (as intermediate targets) that can be use to reduce the development time (the path length to the target)
it is not just about minimizing time or being completely accurate in satisfying the requirements. A combination of these is required
the path to the target is the source code which can be evaluated with make check. The path should fulfill the needs of the developers and can change
the target is the application which can be reached with make. The target should fulfill the needs of the users and can change

@@

\section{Example use case: window manager}
an extreme example of configurable window managers is `ricing' where the window manager is configured mostly for form and not function
fswm targets users with high technical capabilities (therefore no visual indication is needed regarding which window they are in every time etc.)
if keyboard portability is not so important then keycodes are hardcoded for the specific user environment
moreover a window manager should open windows only in full screen
the concept of tiling window managers is oriented towards multitasking
the key shortcuts of a window manager should be predictable by resembling as close as possible most other window managers and development environemnts
the need to be portable across different keyboards demands the use of an additional requirement (xcb-util-keysyms)
the set of functionalities that should be integrated to a window manager are: Enter next/previous window and open program in new window
the windows could be represented as a cyclic doubly linked list
thus C89 was chosen for optimal portability and xcb as the main library
an additional advantage of non-configurability is that the application is ready to be used when installed
